R Notebook

### 2017-08-16 doc/RMD/wmn-differentiation.Rmd
Correct mistake with AMOVA table.
Due to an oversight back in 2014/2015, I had
accidentally flipped the Phi values for the AMOVA
table, rendering the results silly.

This still needs to be fixed in text.

make_amova_table <- function(am, amt, samples = "Region"){
  tot <- nrow(am$results)
  res <- data.frame(list(am$results[-tot, c("Df", "Sum Sq")], 
                         Percent = am$componentsofcovariance[-tot, 2],
                         Pval    = rev(amt$pvalue), 
                         Phi     = am$statphi$Phi[-tot]))
  res <- as.matrix(res)
  colnames(res) <- c("d.f.", "Sum of Squares", "Percent variation", "P", 
                     "Phi statistic")
  names(dimnames(res)) <- c("levels", "statistic")
  rownames(res) <- gsub("samples", samples, rownames(res))
  return(res)
}

@@

```{r AMOVA_table, comment = NA}
make_amova_printable(ssc_amova_table, ssc_amova_newami_table) %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Source", "Between Region within Source", "Within Region"), .before = 1) %>%
  readr::write_csv(path = file.path("results", "tables", "AMOVA-region.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(Hierarchy == "Between Source" ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.1, 0.6, 0.9, 0.9, 1.4)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 100)
```

>>>>

make_amova_table <- function(am, amt, samples = "Region"){
  tot <- nrow(am$results)
  res <- data.frame(list(am$results[-tot, c("Df", "Sum Sq")], 
                         Percent = am$componentsofcovariance[-tot, 2],
                         Pval    = rev(amt$pvalue), 
                         Phi     = rev(am$statphi$Phi[-tot])))
  res <- as.matrix(res)
  colnames(res) <- c("d.f.", "Sum of Squares", "Percent variation", "P", 
                     "Phi statistic")
  names(dimnames(res)) <- c("levels", "statistic")
  rownames(res) <- gsub("samples", samples, rownames(res))
  return(res)
}

@@

```{r AMOVA_table, comment = NA}
make_amova_printable(ssc_amova_table, ssc_amova_newami_table) %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Source", "Between Region within Source", "Within Region"), .before = 1) %>%
  readr::write_csv(path = file.path(PROJHOME, "results", "tables", "AMOVA-region.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(Hierarchy == "Between Source" ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.1, 0.6, 0.8, 0.8, 1.1)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 90)
```
